A Convolutional Neural Network for Outsole Recognition\tnoteref{t1}

### 2019-06-01 paper/paper.Rnw
Additional comments

>>>>

\svp{Pros and cons of confusion matrix here? Maybe we just don't show the actual proportions on the graph? I'd like to discuss this more in person.}
\svp{If we do include the confusion matrix, this section needs to be MUCH more clearly explained for practitioners. Cross-tabulation isn't a common vocab word...}
